Chicago Crime Rates Prediction

### 2022-06-01 chicago_project/report_latex/article.tex
typos in regressor

\subsection{Ridge Regressor model}
Using the already split training set and validation set, a Ridge Regressor model was trained in order to
try to predict the actual amount of crime for a speicific date in a specific period. Due to the shape of 
the data this experiment was not very successful. In general trying to predict the exact amount of crimes
is not really useful and is prone to error.

@@

\begin{figure}[h]
    \label{figure:}
    \includegraphics[scale=0.3]{fig7.png}
    \caption{The data uset for testing}
\end{figure}

@@

The Figures above show the differences between the actual data and the predicted data. It can 
be clearly seen that the model is underfitting and not generating the desired result.

>>>>

\subsection{Ridge Regressor model}
Using the already split training set and validation set, a Ridge Regressor model was trained in order to
try to predict the actual amount of crime for a specific time period and a specific district. Due to the shape of 
the data this experiment was not very successful.

@@

\begin{figure}[h]
    \label{figure:}
    \includegraphics[scale=0.3]{fig7.png}
    \caption{The data used for testing}
\end{figure}

@@

The Figures above show the differences between the actual data and the predicted data. The model is linear, 
so the predicted values form a plane, while the shape of the observations have curves and don't really shape a surface. It can 
be clearly seen that the model is underfitting and not suited for this data set.
For these reasons we did not move forward with hyperparameter tuning for the Linear Ridge Regressor.
